\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-05-17 main.Rmd
spell check; section ref; page break

Plots can be layered. A comparison of sensors can be done by overlaying them in the same calendar pane. Figure \@ref(fig:overlay)) overlays the pedestrian counts for three locations on the same calendar. Differences between the pedestrian patterns at these locations can be more directly compared. For example, the magnitude of the difference in pedestrians at Flagstaff Station at peak hours of commuter can be seen. The big peak in pedestrian counts for special events at Birrarung Marr is clear. Birrarung Marr has a very distinct temporal pattern relative to the other two locations. The nighttime events, such as White Night (third Saturday in February), only affects the foot traffic at the State Library and Birrarung Marr.

@@

Almost any type of plot can be shown in a calendar pane. Most of the full range of plotting capabilities in **ggplot2** is available. An example is shown in Figure \@ref(fig:scatterplot): the panes contain lag scatterplots, constructed with local scaling for each day at Flagstaff Station, where the lagged hourly count is assigned to the `x` argument and the current hourly count to the `y` argument. It indicates strong autocorrelation on weekends, and weak autocorrelation on work days. The the V-shape in the week day graphs, arises when the next hour sees a substantial increase or decrease in counts. This is due to the morning and afternoon commuter patterns in Figure \@ref(fig:fs-2016): the adjacent hours are positively correlated when approaching to the peak hour but negatively correlated when moving away from the peak.

@@

The `frame_calendar()` function described in Section \@ref(sec:algorithm) is a data restructuring function, neatly integrating into a data pipeline but it requires two steps: data transformation and then plot. There is also little freedom to tailor axes and labels, because specialist code needs to be applied.

>>>>

Plots can be layered. A comparison of sensors can be done by overlaying them in the same calendar pane. Figure \@ref(fig:overlay) overlays the pedestrian counts for three locations on the same calendar. Differences between the pedestrian patterns at these locations can be more directly compared. For example, the magnitude of the difference in pedestrians at Flagstaff Station at peak hours of commuter can be seen. The big peak in pedestrian counts for special events at Birrarung Marr is clear. Birrarung Marr has a very distinct temporal pattern relative to the other two locations. The nighttime events, such as White Night (third Saturday in February), only affects the foot traffic at the State Library and Birrarung Marr.

@@

Almost any type of plot can be shown in a calendar pane. Most of the full range of plotting capabilities in **ggplot2** is available. An example is shown in Figure \@ref(fig:scatterplot): the panes contain lag scatterplots, constructed with local scaling for each day at Flagstaff Station, where the lagged hourly count is assigned to the `x` argument and the current hourly count to the `y` argument. It indicates strong autocorrelation on weekends, and weak autocorrelation on work days. The V-shape in the week day graphs arises when the next hour sees a substantial increase or decrease in counts. This is due to the morning and afternoon commuter patterns in Figure \@ref(fig:fs-2016): the adjacent hours are positively correlated when approaching to the peak hour but negatively correlated when moving away from the peak.

@@

The `frame_calendar()` function described in Section \@ref(sec:opt) is a data restructuring function, neatly integrating into a data pipeline but it requires two steps: data transformation and then plot. There is also little freedom to tailor axes and labels, because specialist code needs to be applied.

### 2019-05-17 main.tex
spell check; section ref; page break

Plots can be layered. A comparison of sensors can be done by overlaying them in the same calendar pane. Figure \ref{fig:overlay}) overlays the pedestrian counts for three locations on the same calendar. Differences between the pedestrian patterns at these locations can be more directly compared. For example, the magnitude of the difference in pedestrians at Flagstaff Station at peak hours of commuter can be seen. The big peak in pedestrian counts for special events at Birrarung Marr is clear. Birrarung Marr has a very distinct temporal pattern relative to the other two locations. The nighttime events, such as White Night (third Saturday in February), only affects the foot traffic at the State Library and Birrarung Marr.

@@

Almost any type of plot can be shown in a calendar pane. Most of the full range of plotting capabilities in \textbf{ggplot2} is available. An example is shown in Figure \ref{fig:scatterplot}: the panes contain lag scatterplots, constructed with local scaling for each day at Flagstaff Station, where the lagged hourly count is assigned to the \texttt{x} argument and the current hourly count to the \texttt{y} argument. It indicates strong autocorrelation on weekends, and weak autocorrelation on work days. The the V-shape in the week day graphs, arises when the next hour sees a substantial increase or decrease in counts. This is due to the morning and afternoon commuter patterns in Figure \ref{fig:fs-2016}: the adjacent hours are positively correlated when approaching to the peak hour but negatively correlated when moving away from the peak.

@@

The \texttt{frame\_calendar()} function described in Section \ref{sec:algorithm} is a data restructuring function, neatly integrating into a data pipeline but it requires two steps: data transformation and then plot. There is also little freedom to tailor axes and labels, because specialist code needs to be applied.

>>>>

Plots can be layered. A comparison of sensors can be done by overlaying them in the same calendar pane. Figure \ref{fig:overlay} overlays the pedestrian counts for three locations on the same calendar. Differences between the pedestrian patterns at these locations can be more directly compared. For example, the magnitude of the difference in pedestrians at Flagstaff Station at peak hours of commuter can be seen. The big peak in pedestrian counts for special events at Birrarung Marr is clear. Birrarung Marr has a very distinct temporal pattern relative to the other two locations. The nighttime events, such as White Night (third Saturday in February), only affects the foot traffic at the State Library and Birrarung Marr.

@@

Almost any type of plot can be shown in a calendar pane. Most of the full range of plotting capabilities in \textbf{ggplot2} is available. An example is shown in Figure \ref{fig:scatterplot}: the panes contain lag scatterplots, constructed with local scaling for each day at Flagstaff Station, where the lagged hourly count is assigned to the \texttt{x} argument and the current hourly count to the \texttt{y} argument. It indicates strong autocorrelation on weekends, and weak autocorrelation on work days. The V-shape in the week day graphs arises when the next hour sees a substantial increase or decrease in counts. This is due to the morning and afternoon commuter patterns in Figure \ref{fig:fs-2016}: the adjacent hours are positively correlated when approaching to the peak hour but negatively correlated when moving away from the peak.

@@

The \texttt{frame\_calendar()} function described in Section \ref{sec:opt} is a data restructuring function, neatly integrating into a data pipeline but it requires two steps: data transformation and then plot. There is also little freedom to tailor axes and labels, because specialist code needs to be applied.
